### 2016-11-01 ms/ms.tex
updated box plot figures

\def\affiliation{
  \begin{enumerate}
  \item Department of Environmental Science, Policy, and Management\\
    University of California, Berkeley\\
    130 Mulford Hall\\
    Berkeley, California, USA\\
    94720\\
  \item Berkeley Institute for Data Science (BIDS)\\
    University of California, Berkeley\\
    190 Doe Library \\
    Berkeley, California, USA\\
  \item Department of Entomology\\
    University of California, Riverside\\
    417 Entomology Bldg.\\
    Riverside, California, USA\\
    92521\\
  \item Departamento de Ecologia\\
    Universidade de Sao Paulo\\
    S{\~a}o Paulo, SP, Brazil\\
    05508-900\\
  \end{enumerate}
}

@@

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~\ref{fig:methods}). We develop a method to examine the temporal
turnover of interactions with weightings based on their similarity. We
followed the algorithm of \cite{ahn2010link} to cluster all the
interactions (edges) hierarchically across sites and years based on
their similarity, and build a dendrogram. The interaction similarity
is based how may plants and pollinators (vertices) two edges share
\citep{ahn2010link, kalinka2011linkcomm}. The more species edges
shared in common, the shorter the branch length between them on the
dendrogram.  We next calculated the temporal turnover of interactions
weighted by their similarity, as approximated by ``phylogenetic''
distance \citep{graham2008phylogenetic, picante-2010-1463}. We then
use linear models to test whether the weighted turnover of
interactions varied between assembling and non-assembling networks
\citep{lme4, lmetest}.

@@

We also explored how the robustness to cascading perturbations changed
as the community assembled, using algebraic connectivity --- the
second smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., in prep). Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of species \citep{costa2007characterization, gibert2013spatial}. The
larger the algebraic connectivity, the more sensitive a network is to
cascading perturbations. Perturbations, such as the decrease in abundance of a
plant or pollinator, can have negative consequences
for the species in the network. For example, pollination service provided to planst could decrease following a decrease in
abundance of a pollinator. The affected plants would set less seeds,
and decrease in abundance the subsequent year. Consequently, other pollinators that
depended on those plant species would also be affected, and the effects of this perturbation would
continue to propagate throughout the network, potentially affecting all species in the community. Alternatively, perturbations could
also have a positive effect. For example, the increase in abundance of a
plant species would lead to an increase in resource availability for the pollinators. The examples
of negative perturbations (e.g., resource collapse, disease spreading,
parasites), however, outnumber possible positive perturbations. It is important to point out that both robustness and algebraic connectivity assume that the network is static --- these metrics do not
account for the ability of species to alter their interaction
depending on circumstances and the resource availability.

@@

\clearpage
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{figures/scheme.pdf}
  \caption{Diagram illustrating the analysis to examine the temporal
    turnover of interactions weighted based on their similarity. A, B
    and C are animal species, and Ps are plant species. The dendrogram
    depicts the interaction similarity across years based on the
    number of shared constituent species.}
  \label{fig:methods}
\end{figure}
\clearpage

@@

\begin{figure}
  \centering
  \includegraphics[width=.95\textwidth]{../analysis/changePoint/plotting/communitiesSkanky2.pdf}
  \caption{The module membership between network changing points. Two
    representative assembling hedgerows are depicted. In the top
    panel, species are grouped by community. The bottom panels
    visualize the flow of species between communities between changing
    points. }
  \label{fig:changePoints2}
\end{figure}
\clearpage

>>>>

\def\affiliation{
  \begin{enumerate}
  \item Department of Environmental Science, Policy, and Management\\
    University of California, Berkeley\\
    130 Mulford Hall\\
    Berkeley, California, USA\\
    94720\\
  \item Berkeley Institute for Data Science (BIDS)\\
    University of California, Berkeley\\
    190 Doe Library \\
    Berkeley, California, USA\\
  \item Department of Entomology\\
    University of California, Riverside\\
    417 Entomology Bldg.\\
    Riverside, California, USA\\
    92521\\
  \item Departamento de Ecologia\\
    Universidade de S{\~a}o Paulo\\
    S{\~a}o Paulo, SP, Brazil\\
    05508-900\\
  \end{enumerate}
}

@@

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~ S2). We develop a method to examine the temporal
turnover of interactions with weightings based on their similarity. We
followed the algorithm of \cite{ahn2010link} to cluster all the
interactions (edges) hierarchically across sites and years based on
their similarity, and build a dendrogram. The interaction similarity
is based how may plants and pollinators (vertices) two edges share
\citep{ahn2010link, kalinka2011linkcomm}. The more species edges
shared in common, the shorter the branch length between them on the
dendrogram.  We next calculated the temporal turnover of interactions
weighted by their similarity, as approximated by ``phylogenetic''
distance \citep{graham2008phylogenetic, picante-2010-1463}. We then
use linear models to test whether the weighted turnover of
interactions varied between assembling and non-assembling networks
\citep{lme4, lmetest}.

@@

We also explored how the robustness to cascading perturbations changed
as the community assembled, using algebraic connectivity --- the
second smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., in prep). Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of species \citep{costa2007characterization, gibert2013spatial}. The
larger the algebraic connectivity, the more sensitive a network is to
cascading perturbations. Perturbations, such as the decrease in
abundance of a plant or pollinator, can have negative consequences for
the species in the network. For example, a decrease in abundance of a
pollinator will diminish the pollination services it provides to
plants. The affected plants would set less seeds, and decrease in
abundance the subsequent year. Consequently, other pollinators that
depended on those plant species would also be affected, and the
effects of this perturbation would continue to propagate throughout
the network. Alternatively, perturbations could also have a positive
effect. For example, the increase in abundance of a plant species
would lead to an increase in resource availability for the
pollinators. The examples of negative perturbations (e.g., resource
collapse, disease spreading, parasites), however, outnumber possible
positive perturbations. It is important to note that both robustness
and algebraic connectivity assume that the network is static. They do
not account for the ability of species to alter their interaction
depending on circumstances and the resource availability.

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=.95\textwidth]{../analysis/changePoint/plotting/communitiesSkanky2.pdf}
  \caption{The module membership between network changing points. Two
    representative assembling hedgerows are depicted. In the top
    panel, species are grouped by module. The bottom panels visualize
    the flow of species between modules between changing points. }
  \label{fig:changePoints2}
\end{figure}
\clearpage
